Conversational expectations account for apparent limits on theory of mind use

### 2016-01-29 writing/cogsci-submission/cogsci_keysar.tex
a few questions about analysis

More dramatically, we find that patterns of errors in Exp.~2 diverge significantly from a uniform distribution across items, $\chi^2(7) = 24.8, p < 0.001$. Looking more closely at these patterns, we see that the only items where errors are consistently made are those where the costly over-informative utterance remains ambiguous. For example, in item 5, both the target and distractor are hair brushes: one is round and one is flat. ``Hair brush'' is already a label at the sub-class level. If we remove the two most difficult items (the ``hair brushes'' and the ``erasers''), the total percentage of errors on experimental trials drops from 24\% to 10\% and the percentage of participants making at least one error drops from 61\% to 32\%.

@@

After separately establishing that matchers in Exp.~2 make fewer mistakes, that directors produce more informative utterances, and that informativity captures item-wise variability in error rates, we tested the link between these effects: does label informativity generally predict errors on critical trials? We used a mixed effects logistic regression model to estimate the effect of target and distractor fit on the probability of making a critical error in both experiments, including a random intercept for game ID. We found that participants are less likely to make errors when the target fit is higher, $b = -0.8, z = -4.1, p < 0.001$ and more likely to make errors when the distractor fit is higher, $b = 1.7, z = 3.7, p < 0.001$. In a nested model comparison, we found that a model including item as a fixed effect provides a significantly better fit, $\chi^2(7) = 16.4, p = 0.022$.

@@

\begin{figure}[t!]
\begin{center}
\includegraphics[scale=.1]{images/itemwisefitness.jpeg}
\caption{Item-wise error rates compared with label fitness ratios. Error bars are bootstrapped 95\% confidence intervals for fitness and 95\% highest density intervals for error rates.}
\label{fig:itemLevel}
\end{center}
\end{figure}

>>>>

We find that patterns of errors in Exp.~2 diverge significantly from a uniform distribution across items, $\chi^2(7) = 24.8, p < 0.001$. Looking more closely at these patterns, we see that the only items where errors are consistently made are those where the more precise utterances used remain ambiguous. For example, in item 5, both the target and distractor are hair brushes: one is round and one is flat. ``Hair brush'' is already a label at the sub-class level. If we remove the two most difficult items (the ``hair brushes'' and the ``erasers''), the total percentage of errors on experimental trials drops from 24\% to 10\% and the percentage of participants making at least one error drops from 61\% to 32\%.

@@

After separately establishing that matchers in Exp.~2 make fewer mistakes, that directors produce more informative utterances, and that informativity captures item-wise variability in error rates, we tested the link between these effects: does label informativity generally predict errors on critical trials? We used a mixed effects logistic regression model to estimate the effect of target and distractor fit on the probability of making a critical error in both experiments, including a random intercept for game ID. We found that participants are less likely to make errors when the target fit is higher, $b = -0.8, z = -4.1, p < 0.001$ and more likely to make errors when the distractor fit is higher, $b = 1.7, z = 3.7, p < 0.001$. In a nested model comparison, we found that a model including item as a fixed effect provides a significantly better fit, $\chi^2(7) = 16.4, p = 0.022$. 
\ndg{remind me (and reader) what this model comparison means?}

@@

\begin{figure}[t!]
\begin{center}
\includegraphics[scale=.1]{images/itemwisefitness.jpeg}
\caption{Item-wise error rates compared with label fitness ratios. Error bars are bootstrapped 95\% confidence intervals for fitness and 95\% highest density intervals for error rates.
\ndg{is this expt 1 or 2 data? say ratio is scaled to unit interval in order to compare visually to error rates?}
}
\label{fig:itemLevel}
\end{center}
\end{figure}
